Bird beak's elaboration and exploration

### 2021-09-24 Analysis/03-elaboration_exploration_analyses.Rmd
Update 03-elaboration_exploration_analyses.Rmd

and the eigenvectors **v** and the eigenvalues $\lambda$ satisfying the following eigen decomposition:

\begin{equation}
    VCV_{n} \bold{v} = \lambda \bold{v}
\end{equation}

We can get $M_{n}$ matrix containing all the edge coordinates of the 0.95 CI hypersphere from $VCV_{n}$ using the transposition of the cross product between the eigenvectors **v** and the product of the scaled 0.95 CI unit sphere $O'_{n}$ and the eigenvalues $\lambda$:

\begin{equation}
    M_{n} = [(O'_{n}\sqrt{\lambda}) \times \bold{v}]^{\text{T}}
\end{equation}

>>>>

and the eigenvectors *v* and the eigenvalues $\lambda$ satisfying the following eigen decomposition:

\begin{equation}
    VCV_{n} v = \lambda v
\end{equation}

We can get $M_{n}$ matrix containing all the edge coordinates of the 0.95 CI hypersphere from $VCV_{n}$ using the transposition of the cross product between the eigenvectors *v* and the product of the scaled 0.95 CI unit sphere $O'_{n}$ and the eigenvalues $\lambda$:

\begin{equation}
    M_{n} = [(O'_{n}\sqrt{\lambda}) \times v]^{\text{T}}
\end{equation}
